%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventryWithTags
    {Ph.D. Research Assistant} % Job title
    {University of British Columbia} % Organization
    {Vancouver, Canada} % Location
    {Sep \ 2014 -- May \ 2020} % Date(s)
    {\fbox{Python} \fbox{C++} \fbox{NumPy} \fbox{pandas} \fbox{Bash} \fbox{Matplotlib} \fbox{Machine learning} \fbox{Batch processing} \fbox{Statistics} \fbox{\LaTeX}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Used the NumPy and pandas Python libraries and the C++ \hypersetup{urlcolor=blue}\href{https://root.cern.ch/}{ROOT} framework to analyze data collected by the BaBar detector.}
      \item {Improved the limit on a parameter of a hypothesized new fundamental particle by a factor of 3--10 (depending on mass). The limit was set using Bayesian statistical methods.}
        \item {Applied machine learning methods to improve photon identification by up to \SI{25}{\percent} in the Belle II experiment.}
        \item {Contributed to code maintenance and unit tests of the Belle II experiment's Python and C++ code base (non public).}
      \end{cvitems}
    }

    \cventryWithTags
    {Physicist / System engineer} % Job title
    {Elbit Systems Ltd., Research and Development department} % Organization
    {Haifa, Israel} % Location
    {Jun \ 2012 -- Jul \ 2014} % Date(s)
    {\fbox{MATLAB} \fbox{Algorithms} \fbox{Sensors}}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In charge of calibrating inertial measurement units (IMU) consisting of gyroscopes, accelerometers and magnetometers.}
        \item {Maintained the calibration software written in MATLAB.}
        \item {Commissioned a new rate table built in order to improve IMU calibration capabilities.}
        \item {System engineer for a tracker utilizing several different
          technologies to determine position and orientation. The tracker is incorporated into several of Elbit's products, for example, a pilot helmet that tracks head movements.}
        \item {In charge of assigning tasks to algorithm, software, hardware, mechanical and material teams and evaluating progress.}
      \end{cvitems}
    }

    \cventryWithTags
    {M.Sc. Research Assistant} % Job title
    {Technion -- Israel Institute of Technology} % Organization
    {Haifa, Israel} % Location
    {Oct \ 2007 -- Dec \ 2010} % Date(s)
    {\fbox{C++} \fbox{Bash} \fbox{Batch processing} \fbox{Statistics} \fbox{\LaTeX}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed simulations of data from the ATLAS detector using the C++ \hypersetup{urlcolor=blue}\href{https://root.cern.ch/}{ROOT} framework.}
        \item {Determine that it is feasible to measure the $B_c$ particle's lifetime without detecting all of its decay products.}
        \item {3000 signal-like events were filtered out of 1.35 million background events.}
        \item {Used statistical tools to determine the $B_c$ lifetime and statistical error.}
        \item {Predicted the number of ATLAS collision events necessary in order for the precision of such a measurement to surpass the most accurate single measurement in the world.}
      \end{cvitems}
    }
    %---------------------------------------------------------
  \end{cventries}
